Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-02-13 text/paper2/ms.tex
comment out figures
intro

\title{Inferring the gravitational potential of the Milky Way with a few precisely measured stars}
\author{Adrian M. Price-Whelan, David W. Hogg, Kathryn V. Johnston, [TODO: order?]}

@@

Cosmological simulations of galaxy formation in the $\Lambda$CDM paradigm predict dark matter halos that (1) are permeated with substructure on many scales, (2) are triaxial in shape, and (3) have density profiles and shapes that vary with radius \citep{dubinski91, jing02, kuhlen07, veraciro11}. Dark-matter-only simulations produce strongly triaxial halos \citep{} with large density variations \citep{zemp09}. Including baryons tends to soften the triaxiality in the inner galaxy \citep[e.g.,][]{dubinski94, pontzen12} but does not erase the clumpy, triaxial nature of the outer halo. This leads to radially-dependent axis ratios and orientation, density profiles, and smoothness, thus predicting complicated, non-intregrable potential forms for Milky Way-like galaxies.

>>>>

\title{Inferring the gravitational potential of the Milky Way with a few precisely measured stars}
\author{Adrian M. Price-Whelan, David W. Hogg, Kathryn V. Johnston}

@@

Cosmological simulations of galaxy formation in the $\Lambda$CDM paradigm predict dark matter halos that (1) are permeated with substructure on many scales, (2) are triaxial in shape, and (3) have density profiles and shapes that vary with radius \citep{dubinski91, jing02, kuhlen07, veraciro11}. Dark-matter-only simulations produce strongly triaxial halos \citep{} with large density variations \citep{zemp09}. Including baryons tends to soften the triaxiality and graininess in the inner galaxy \citep[e.g.,][]{dubinski94, pontzen12} but does not erase the clumpy, triaxial nature of the outer halo. This leads to radially-dependent axis ratios and orientation, density profiles, and smoothness, thus predicting complicated, non-intregrable potential forms for Milky Way-like galaxies.
